Cryptanalysis of \MORUS

### 2018-05-10 morusAC_01_Introduction.tex
added sentence about ignoring rotation constants in contributions

To the best of our knowledge, this is the first attack on full \MORUS in the nonce-respecting setting.
We also note that rekeying does not prevent the attack: the biases are independent of the secret encryption key and nonce, and can be exploited as long as a given plaintext segment is encrypted sufficiently often, regardless of whether each encryption uses a different key.

>>>>

To the best of our knowledge, this is the first attack on full \MORUS in the nonce-respecting setting.
We note that rekeying does not prevent the attack: the biases are independent of the secret encryption key and nonce, and can be exploited as long as a given plaintext segment is encrypted sufficiently often, regardless of whether each encryption uses a different key.
A surprising feature of the linear trail underpinning our attack is also that it does not depend on the values of rotation constants: a very similar trail would exist for most choices of round constants.
